Democratizing Secure Two-Party Computation

### 2017-10-13 OaklandSubmission/intro.tex
minor

Suppose a developer wants to compute $w^Tx >0$ securely using SMC. With the current techniques, he has two options.  
\begin{tiret}
\item He can code up the functionality in a programmer friendly domain-specific language such as \cite{lambdaps,wysteria,oblivm} that would automatically compile it to an SMC protocol. The downside is that all of these works build on a cryptographic back-end that is either entirely boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}. The efficiency of the generated SMC protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an Arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations.
\item To address this issue, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations. \footnote{Need to note somewhere that many works combined HE and Yao. Look at ABY for references.}
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of complex trade-offs between arithmetic and boolean cryptographic schemes and split the functionality into such parts accordingly. In their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate conversion gates. In short, the current system of ABY is not suitable to be used by non-specialist programmers.

>>>>

Suppose a developer wants to compute $w^Tx >0$ securely using SMC. With the current techniques, he has two options.  
\begin{tiret}
\item He can code up the functionality in a programmer friendly domain-specific language such as \cite{lambdaps,wysteria,oblivm,smcl} that would automatically compile it to an SMC protocol. The downside is that all of these works build on a cryptographic back-end that is either entirely boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}. The efficiency of the generated SMC protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an Arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations.
\item To address this issue, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations. \footnote{Need to note somewhere that many works combined HE and Yao. Look at ABY for references.}
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of complex trade-offs between arithmetic and boolean cryptographic schemes and split the functionality into such parts accordingly. In their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate conversion gates. In short, the current system of ABY is not suitable to be used by non-specialist programmers.
